First Measurements of the D(e,e'p)n Cross Section at \\ Very High Recoil Momenta and Large Q$^{2}$

### 2020-02-11 MY_PUBLICATIONS/PRL/draft_v4_HCsuggestions/body.tex
updated

$\vec{p_{r}} = \vec{q} - \vec{p_{f}}$ and the missing  energy as $E_{m} = \omega - T_{p} - T_{r}$ where $\vec{p_{f}}$ is the final proton momentum, $\vec{q}$ is the 3-momentum transfer and $(T_{p}$ and $T_{r})$ are the

@@

\indent We measured three central missing momentum settings: $p_{r}=80,580$ and $750$ MeV/c. At each of these settings, the electron arm (SHMS) was fixed and the proton arm (HMS) was rotated from smaller to larger angles corresponding to the
the lower and higher missing momentum settings, respectively. At these kinematic settings, the 3-momentum transfer covered a range of $2.4\lesssim|\vec{q}|\lesssim3.2$ GeV/c which is more than twice the highest neutron recoil momentum ($p_{r}$)

@@

\indent Hydrogen elastic $^{1}H(e,e'p)$ data was also taken at kinematics close to the deuteron $p_{r}=80$ MeV/c setting for cross-checks with the spectrometer acceptance model using the  Hall C Monte Carlo
simulation program, SIMC. Additional $^{1}H(e,e'p)$ data were also taken at three other kinematic settings that covered the SHMS momentum acceptance range for the deuteron and were used for spectrometer optics optimization, 

@@

energy cut (peak $\sim$ 2.22 MeV for the deuteron) to select true $^{2}H(e,e'p)n$ coincidences, a coincidence time cut to select true coincidence events and not accidentals,  a PID cut on the

@@

\indent The experimental data yields for both hydrogen and deuteron data were normalized by the total charge and corrected for various inefficiencies. For $^{2}H(e,e'p)n$ the corrections

@@

\indent For $^{1}H(e,e'p)$, the corrected data yield was compared to SIMC calculations using J. Arrington's proton form factor parametrization\cite{PhysRevC.69.022201} to check the spectrometer acceptance
model. The ratio of data to simulation yield was determined to be $97.6\pm0.3 \%$ (statistical uncertainty only). For $^{2}H(e,e'p)n$, the low missing momentum data ($p_{r}=80$ MeV/c) were compared to the Hall A data (See Fig. \ref{fig:fig1}).

@@

\indent The systematic uncertainties due to our limited knowledge of the beam energy and spectrometer angle/momentum settings were determined point-to-point in ($\theta_{nq}, p_{r}$) bins for each data set independently, and added in quadrature for overlapping $p_{r}$ bins
of different data sets. For $\theta_{nq}= 35^{o}, 45^{o}$ and $75^{o}$ (presented on this Letter) the overall kinematic uncertainty varied up to 6.5$\%$ for $p_{r}\leq1.01$ GeV/c.

@@

\indent The data were radiatively corrected for each bin in ($\theta_{nq}, p_{r}$) by multiplying the measured cross sections by the ratio of the calculated particle yield excluding and including radiative effects. The Monte-Carlo code SIMC was used for these calculations with the Deuteron Model by J.M.Laget including FSI~\cite{LAGET2005}.
For each bin in ($\theta_{nq}, p_{r}$), the averaged $^{2}H(e,e'p)n$ kinematics has been calculated and used in the bin centering correction factor defined as:
$f_{bc} \equiv \sigma_{avg.kin} / \bar{\sigma}$, where $\sigma_{avg.kin}$ is the cross section calculated at the averaged kinematics and $\bar{\sigma}$ is the cross section averaged

@@

for overlapping bins in $p_{r}$. The reduced cross sections are defined as follows:

@@

\sigma_{red} \equiv \frac{\sigma_{exp(th)}}{Kf_{rec}\sigma_{cc1}}

@@

where $\sigma_{exp(th)}$ is the 5-fold experimental (or theoretical) differential cross section $\frac{d^{5}\sigma}{d\omega d\Omega_{e} d\Omega_{p}}$, $K$ is a kinematical factor, $f_{rec}$ is the recoil factor  and $\sigma_{cc1}$ is the de Forest\cite{DEFOREST1983} electron-proton off-shell cross section calculated using the form factor parametrization of Ref.\cite{PhysRevC.69.022201}.
Within the PWIA, $\sigma_{red}$ corresponds to the proton momentum distribution inside the deuteron. \\

@@

$p_{r}$ for three recoil angle settings at

@@

\caption{The reduced cross sections $\sigma_{red}(p_{r})$ as a function of neutron recoil momentum $p_{r}$ are shown in (a)-(c) for recoil angles $\theta_{nq}=35^{o}, 45^{o}$ and $75^{o}$, respectively,

@@

\indent For all recoil angles shown in Fig. \hyperref[fig:fig1]{1} at recoil momenta $p_{r}\leq300$ MeV/c the cross sections are well reproduced  by  all models when FSI are included.
The agreement at $p_{r}\leq300$ MeV/c can be understood from the fact that this region corresponds to the long-range part of the NN potential where the One Pion Exchange Potential (OPEP)

@@

\indent Beyond $p_{r}\sim300$ MeV/c at $\theta_{nq}=35^{o}$ and $45^{o}$ [Figs. \hyperref[fig:fig1]{1(a), 1(b)}], the Paris and
AV18 models significantly differ from the CD-Bonn. In this region, the Paris/AV18 cross sections are dominated by the PWIA and within good agreement of each other up $p_{r}\sim700$ MeV/c. The CD-Bonn cross sections in contrast are generally smaller than the Paris/AV18 in this region.  In addition for $\theta_{nq}=35^{o}$ they are dominated by the PWIA up to $p_{r}\sim800$ MeV/c [Fig. \hyperref[fig:fig1]{1(a)}]  while for $\theta_{nq}=45^{o}$  FSI start to contribute already above 600 MeV/c [Fig. \hyperref[fig:fig1]{1(b)}].

@@

\indent At $\theta_{nq}=75^{o}$ [Fig. \hyperref[fig:fig1]{1(c)}] and $p_{r}>300$ MeV/c, FSI become the dominant contributions to the cross sections for all models which exhibit a similar

@@

\indent To quantify the discrepancy observed between data and theory in Fig. \ref{fig:fig1}, the ratio of the experimental and theoretical reduced cross sections ($\sigma_{red}$) to the
deuteron momentum distribution  calculated using the CD-Bonn potential ($\sigma^{\text{CD-Bonn PWIA}}_{red}$)\cite{PhysRevC.63.024001} is shown in Fig. \ref{fig:fig2}. \\
\indent For $\theta_{nq}=35^{o}$ and $45^{o}$ [Figs. \hyperref[fig:fig2]{2(a),(b)}] the data are best described by the CD-Bonn PWIA calculation for recoil momenta up
to $p_{r}\sim700$ MeV/c and $\sim600$ MeV/c, respectively. Furthermore, the agreement between the Halls A and C data solidifies the Hall A approach of selecting a kinematic

@@

\caption{The ratio R($p_{r}$) = $\sigma_{red}/\sigma^{{\text{CD-Bonn PWIA}}}_{red}$ is shown in (a)-(c) for $\theta_{nq}=35^{o}, 45^{o}$ and $75^{o}$, respectively, each with a bin width of $\pm 5^{o}$.

@@

\indent At $\theta_{nq}=75^{o}$ [Fig. \hyperref[fig:fig2]{2(c)}], FSI are small below $p_{r}\sim150$ MeV/c, but do not exactly cancel the PWIA/FSI interference term in the scattering amplitude which results in a small dip in this region in agreement with the data.
At $p_{r}>300$ MeV/c, the data was statistically limited as our focus was on the smaller recoil angles. The Hall A data, however, shows a reasonable agreement with the FSI from all models which gives us confidence in our understanding

@@

\indent This experiment extended the previous Hall A cross section measurements on the $^{2}H(e,e'p)n$ reaction to 

@@

Furthermore, the CD-Bonn model was found to be significantly different than the Paris or AV18 models and was able to partially describe the data over a larger range in $p_{r}$.

@@

to the equipment for the Hall C upgrade making all four commissioning experiments possible.

>>>>

$\vec{p_{\mathrm{r}}} = \vec{q} - \vec{p_{\mathrm{f}}}$ and the missing  energy as $E_{\mathrm{m}} = \omega - T_{p} - T_{\mathrm{r}}$ where $\vec{p_{\mathrm{f}}}$ is the final proton momentum, $\vec{q}$ is the 3-momentum transfer and $(T_{p}$ and $T_{\mathrm{r}})$ are the

@@

\indent We measured three central missing momentum settings: $p_{\mathrm{r}}=80,580$ and $750$ MeV/c. At each of these settings, the electron arm (SHMS) was fixed and the proton arm (HMS) was rotated from smaller to larger angles corresponding to the
the lower and higher missing momentum settings, respectively. At these kinematic settings, the 3-momentum transfer covered a range of $2.4\lesssim|\vec{q}|\lesssim3.2$ GeV/c which is more than twice the highest neutron recoil momentum ($p_{\mathrm{r}}$)

@@

\indent Hydrogen elastic $^{1}\mathrm{H}(e,e'p)$ data was also taken at kinematics close to the deuteron $p_{\mathrm{r}}=80$ MeV/c setting for cross-checks with the spectrometer acceptance model using the  Hall C Monte Carlo
simulation program, SIMC. Additional $^{1}\mathrm{H}(e,e'p)$ data were also taken at three other kinematic settings that covered the SHMS momentum acceptance range for the deuteron and were used for spectrometer optics optimization, 

@@

energy cut (peak $\sim$ 2.22 MeV for the deuteron) to select true $^{2}\mathrm{H}(e,e'p)n$ coincidences, a coincidence time cut to select true coincidence events and not accidentals,  a PID cut on the

@@

\indent The experimental data yields for both hydrogen and deuteron data were normalized by the total charge and corrected for various inefficiencies. For $^{2}\mathrm{H}(e,e'p)n$ the corrections

@@

\indent For $^{1}\mathrm{H}(e,e'p)$, the corrected data yield was compared to SIMC calculations using J. Arrington's proton form factor parametrization\cite{PhysRevC.69.022201} to check the spectrometer acceptance
model. The ratio of data to simulation yield was determined to be $97.6\pm0.3 \%$ (statistical uncertainty only). For $^{2}\mathrm{H}(e,e'p)n$, the low missing momentum data ($p_{\mathrm{r}}=80$ MeV/c) were compared to the Hall A data (See Fig. \ref{fig:fig1}).

@@

\indent The systematic uncertainties due to our limited knowledge of the beam energy and spectrometer angle/momentum settings were determined point-to-point in ($\theta_{nq}, p_{\mathrm{r}}$) bins for each data set independently, and added in quadrature for overlapping $p_{\mathrm{r}}$ bins
of different data sets. For $\theta_{nq}= 35^{o}, 45^{o}$ and $75^{o}$ (presented in this Letter) the overall kinematic uncertainty varied up to 6.5$\%$ for $p_{\mathrm{r}}\leq1.01$ GeV/c.

@@

\indent The data were radiatively corrected for each bin in ($\theta_{nq}, p_{\mathrm{r}}$) by multiplying the measured cross sections by the ratio of the calculated particle yield excluding and including radiative effects. The Monte-Carlo code SIMC was used for these calculations with the Deuteron Model by J.M.Laget including FSI~\cite{LAGET2005}.
For each bin in ($\theta_{nq}, p_{\mathrm{r}}$), the averaged $^{2}\mathrm{H}(e,e'p)n$ kinematics has been calculated and used in the bin centering correction factor defined as:
$f_{\mathrm{bc}} \equiv \sigma_{\mathrm{avg.kin}} / \bar{\sigma}$, where $\sigma_{\mathrm{avg.kin}}$ is the cross section calculated at the averaged kinematics and $\bar{\sigma}$ is the cross section averaged

@@

for overlapping bins in $p_{\mathrm{r}}$. The reduced cross sections are defined as follows:

@@

\sigma_{\mathrm{red}} \equiv \frac{\sigma_{\mathrm{exp(th)}}}{Kf_{\mathrm{rec}}\sigma_{\mathrm{cc1}}}

@@

where $\sigma_{\mathrm{exp(th)}}$ is the 5-fold experimental (or theoretical) differential cross section $\frac{d^{5}\sigma}{d\omega d\Omega_{e} d\Omega_{p}}$, $K$ is a kinematical factor, $f_{\mathrm{rec}}$ is the recoil factor  and $\sigma_{\mathrm{cc1}}$ is the de Forest\cite{DEFOREST1983} electron-proton off-shell cross section calculated using the form factor parametrization of Ref.\cite{PhysRevC.69.022201}.
Within the PWIA, $\sigma_{\mathrm{red}}$ corresponds to the proton momentum distribution inside the deuteron. \\

@@

$p_{\mathrm{r}}$ for three recoil angle settings at

@@

\caption{The reduced cross sections $\sigma_{\mathrm{red}}(p_{\mathrm{r}})$ as a function of neutron recoil momentum $p_{\mathrm{r}}$ are shown in (a)-(c) for recoil angles $\theta_{nq}=35^{o}, 45^{o}$ and $75^{o}$, respectively,

@@

\indent For all recoil angles shown in Fig. \hyperref[fig:fig1]{1} at recoil momenta $p_{\mathrm{r}}\leq300$ MeV/c the cross sections are well reproduced  by  all models when FSI are included.
The agreement at $p_{\mathrm{r}}\leq300$ MeV/c can be understood from the fact that this region corresponds to the long-range part of the NN potential where the One Pion Exchange Potential (OPEP)

@@

\indent Beyond $p_{\mathrm{r}}\sim300$ MeV/c at $\theta_{nq}=35^{o}$ and $45^{o}$ (Figs. \hyperref[fig:fig1]{1(a), 1(b)}), the Paris and
AV18 models significantly differ from the CD-Bonn. In this region, the Paris/AV18 cross sections are dominated by the PWIA and within good agreement of each other up $p_{\mathrm{r}}\sim700$ MeV/c. The CD-Bonn cross sections in contrast are generally smaller than the Paris/AV18 in this region.  In addition for $\theta_{nq}=35^{o}$ they are dominated by the PWIA up to $p_{\mathrm{r}}\sim800$ MeV/c (Fig. \hyperref[fig:fig1]{1(a)})  while for $\theta_{nq}=45^{o}$  FSI start to contribute already above 600 MeV/c (Fig. \hyperref[fig:fig1]{1(b)}).

@@

\indent At $\theta_{nq}=75^{o}$ (Fig. \hyperref[fig:fig1]{1(c)}) and $p_{\mathrm{r}}>180$ MeV/c, FSI become the dominant contributions to the cross sections for all models which exhibit a similar

@@

\indent To quantify the discrepancy observed between data and theory in Fig. \ref{fig:fig1}, the ratio of the experimental and theoretical reduced cross sections ($\sigma_{\mathrm{red}}$) to the
deuteron momentum distribution  calculated using the CD-Bonn potential ($\sigma^{\text{CD-Bonn PWIA}}_{\mathrm{red}}$)\cite{PhysRevC.63.024001} is shown in Fig. \ref{fig:fig2}. \\
\indent For $\theta_{nq}=35^{o}$ and $45^{o}$ (Figs. \hyperref[fig:fig2]{2(a),(b)}) the data are best described by the CD-Bonn PWIA calculation for recoil momenta up
to $p_{\mathrm{r}}\sim700$ MeV/c and $\sim600$ MeV/c, respectively. Furthermore, the agreement between the Halls A and C data solidifies the Hall A approach of selecting a kinematic

@@

\caption{The ratio $R(p_{\mathrm{r}}$) = $\sigma_{\mathrm{red}}/\sigma^{{\text{CD-Bonn PWIA}}}_{\mathrm{red}}$ is shown in (a)-(c) for $\theta_{nq}=35^{o}, 45^{o}$ and $75^{o}$, respectively, each with a bin width of $\pm 5^{o}$.

@@

\indent At $\theta_{nq}=75^{o}$ (Fig. \hyperref[fig:fig2]{2(c)}), FSI are small below $p_{\mathrm{r}}\sim180$ MeV/c, but do not exactly cancel the PWIA/FSI interference term in the scattering amplitude which results in a small dip in this region in agreement with the data.
At $p_{\mathrm{r}}>300$ MeV/c, the data was statistically limited as our focus was on the smaller recoil angles. The Hall A data, however, shows a reasonable agreement with the FSI from all models which gives us confidence in our understanding

@@

\indent This experiment extended the previous Hall A cross section measurements on the $^{2}\mathrm{H}(e,e'p)n$ reaction to 

@@

Furthermore, the CD-Bonn model was found to be significantly different than the Paris or AV18 models and was able to partially describe the data over a larger range in $p_{\mathrm{r}}$.

@@

to the equipment for the Hall C upgrade, making all four commissioning experiments possible. This work
was supported in part by the U.S. Department of Energy (DOE), Office of Science, Office of Nuclear Physics
under grant No. D2-SC0013620 and contract DE-AC05-06OR23177, the Nuclear Regulatory Commission (NRC) Fellowship
under grant No. NRC-HQ-84-14-G-0040 and the Doctoral Evidence Acquisition (DEA) Fellowship.

### 2020-02-11 MY_PUBLICATIONS/PRL/draft_v4_HCsuggestions/introduction.tex
updated

electro-disintegration reaction at very high neutron recoil (or missing) momenta. Within the plane wave impulse approximation (PWIA), the virtual photon couples to

@@

to the initial state proton, $\vec{p}_{r} = -\vec{p}_{i,p}$, thus providing information on the momentum of the bound nucleon and its momentum distribution. 
In reality, the ejected nucleon undergoes final state interactions (FSI) corresponding to subsequent interactions with the recoiling system. Another possibility is that the
photon couples to the virtual meson being exchanged between nucleons (meson exchange currents), or that the photon excites a bound nucleon into a resonance state which subsequently
decays back into its ground state (isobar configurations).  FSI, meson exchange currents (MEC) and isobar configurations (IC)  can significantly alter the recoiling neutron

@@

\indent Theoretically, MEC and IC are expected to be suppressed at $Q^{2}>1$ (GeV/c)$^{2})$ and Bjorken $x_{Bj}\equiv Q^{2}/2M_{p}\omega>1$, where $M_{p}$ and $\omega$ are the proton mass and photon energy transfer, respectively.
The suppression of MEC can be understood from the fact that the estimated MEC scattering amplitude is proportional to  $(1 + Q^{2}/m^{2}_{meson})^{-2}(1+Q^{2}/\Lambda^{2})^{-2}$, where $m_{meson}\approx0.71$ GeV/c$^{2}$ and
$\Lambda^{2}\sim 0.8-1 $ (GeV/c)$^{2}$\cite{Sargsian_2001}. IC can be suppressed kinematically by selecting $x_{Bj}>1$, where one probes the lower energy part of the deuteron quasi-elastic peak which is maximally far away from the inelastic resonance

@@

\indent Previous deuteron electro-disintegration experiments performed at lower $Q^{2}$ ($Q^{2}<1$ (GeV/c)$^{2}$)[See Section 5 of Ref. \cite{sargsian_2015}] have helped quantify the contributions
from FSI, MEC and IC on the $^{2}H(e,e'p)n$ cross-section and to determine the kinematics at which they are either suppressed (MEC and IC) or under control (FSI).  \\

@@

GEA predicts FSI to be maximal for $\theta_{nq}\sim70^{o}$. This strong angular dependence has been found to lead to the cancellation of FSI at neutron recoil angles around $\theta_{nq}\sim40^{o}$ and $\theta_{nq}\sim120^{o}$. Since at $\theta_{nq}\sim120^{o}$ IC are not negligible, $x_{Bj}>1$ (or equivalently $\theta_{nq}\sim40^{o}$) is the preferred choice to suppress IC as well as FSI. \\

@@

\indent The first $^{2}H(e,e'p)n$ experiments at high $Q^{2}$ were carried out at Jefferson Lab (JLab) in Halls A\cite{PhysRevLett.107.262501} and B\cite{PhysRevLett.98.262502}. Both

@@

\indent In Hall A, the pair of high resolution spectrometers (HRS) made it possible to measure the missing  momentum dependence of the cross section for fixed neutron recoil angles ($\theta_{nq}$) reaching missing momenta up to $p_{r}=550$ MeV/c. For the first time very different momentum distributions were found for $\theta_{nq}=35\pm5^{o}$

@@

\indent The experiment presented in this Letter takes advantage of the kinematic window previously found in the Hall A experiment and extends the $^{2}H(e,e'p)n$ cross section measurements

>>>>

electro-disintegration reaction at very high neutron recoil (or missing) momenta. Within the PWIA, the virtual photon couples to

@@

to the initial state proton, $\vec{p}_{\mathrm{r}} = -\vec{p}_{\mathrm{i},p}$, thus providing information on the momentum of the bound nucleon and its momentum distribution. 
In reality, the ejected nucleon undergoes FSI corresponding to subsequent interactions with the recoiling system. Another possibility is that the
photon couples to the virtual meson being exchanged between nucleons (MEC), or that the photon excites a bound nucleon into a resonance state which subsequently
decays back into its ground state (IC).  FSI, MEC and IC can significantly alter the recoiling neutron

@@

\indent Theoretically, MEC and IC are expected to be suppressed at $Q^{2}>1$ (GeV/c)$^{2})$ and Bjorken $x_{\mathrm{Bj}}\equiv Q^{2}/2M_{p}\omega>1$, where $M_{p}$ and $\omega$ are the proton mass and photon energy transfer, respectively.
The suppression of MEC can be understood from the fact that the estimated MEC scattering amplitude is proportional to  $(1 + Q^{2}/m^{2}_{\mathrm{meson}})^{-2}(1+Q^{2}/\Lambda^{2})^{-2}$, where $m_{\mathrm{meson}}\approx0.71$ GeV/c$^{2}$ and
$\Lambda^{2}\sim 0.8-1 $ (GeV/c)$^{2}$\cite{Sargsian_2001}. IC can be suppressed kinematically by selecting $x_{\mathrm{Bj}}>1$, where one probes the lower energy part of the deuteron quasi-elastic peak which is maximally far away from the inelastic resonance

@@

\indent Previous deuteron electro-disintegration experiments performed at lower $Q^{2}$ ($Q^{2}<1$ (GeV/c)$^{2}$)(See Section 5 of Ref. \cite{sargsian_2015}) have helped quantify the contributions
from FSI, MEC and IC on the $^{2}\mathrm{H}(e,e'p)n$ cross-section and to determine the kinematics at which they are either suppressed (MEC and IC) or under control (FSI).  \\

@@

GEA predicts FSI to be maximal for $\theta_{nq}\sim70^{o}$. This strong angular dependence has been found to lead to the cancellation of FSI at neutron recoil angles around $\theta_{nq}\sim40^{o}$ and $\theta_{nq}\sim120^{o}$. Since at $\theta_{nq}\sim120^{o}$ IC are not negligible, $x_{\mathrm{Bj}}>1$ (or equivalently $\theta_{nq}\sim40^{o}$) is the preferred choice to suppress IC as well as FSI. \\

@@

\indent The first $^{2}\mathrm{H}(e,e'p)n$ experiments at high $Q^{2}$ were carried out at Jefferson Lab (JLab) in Halls A\cite{PhysRevLett.107.262501} and B\cite{PhysRevLett.98.262502}. Both

@@

\indent In Hall A, the pair of high resolution spectrometers (HRS) made it possible to measure the missing  momentum dependence of the cross section for fixed neutron recoil angles ($\theta_{nq}$) reaching missing momenta up to $p_{\mathrm{r}}=550$ MeV/c. For the first time very different momentum distributions were found for $\theta_{nq}=35\pm5^{o}$

@@

\indent The experiment presented in this Letter takes advantage of the kinematic window previously found in the Hall A experiment and extends the $^{2}\mathrm{H}(e,e'p)n$ cross section measurements

### 2020-02-11 MY_PUBLICATIONS/PRL/draft_v4_HCsuggestions/prl.tex
updated

% The following information is for internal review, please remove them for submission
\widetext
\leftline{Version 03 as of \today}
\leftline{Primary authors: Carlos Yero, Werner Boeglin, Mark Jones}
\leftline{To be submitted to PRL}
\leftline{Comment to {\tt cyero002@fiu.edu} by xxx, yyy}
\centerline{INTERNAL DOCUMENT -- NOT FOR PUBLIC DISTRIBUTION}

@@

\begin{abstract}
  New $^{2}H(e,e'p)n$ cross sections have been measured at 4-momentum transfers of $Q^{2} = 4.5 \pm 0.5$ (GeV/c)$^{2}$
  reaching neutron recoil (missing) momenta up $p_{r}\sim$ 1.01 GeV/c. The data have been obtained at fixed neutron recoil angles
$\theta_{nq} = 35^\circ$ and $45^\circ$  with respect to the 3-momentum
transfer, $\vec q$. At these kinematic settings final state interactions (FSI),
meson exchange currents (MEC) and isobar configurations (IC) are expected to 
be suppressed and the plane wave impulse approximation (PWIA) provides the
dominant cross section contribution. The new data are compared to recent
theoretical calculations where a significant disagreement at very high
missing momenta has been observed.

>>>>

% The following information is for internal review, please remove them for submission
\widetext
\leftline{Version 03 as of \today}
\leftline{Primary authors: Carlos Yero, Werner Boeglin, Mark Jones}
\leftline{To be submitted to PRL}
\leftline{Comment to {\tt cyero002@fiu.edu, \tt boeglinw@fiu.edu, \tt jones@jlab.org} by March 02, 2020}
\centerline{INTERNAL DOCUMENT -- NOT FOR PUBLIC DISTRIBUTION}

@@

\begin{abstract}
  New $^{2}\mathrm{H}(e,e'p)n$ cross sections have been measured at 4-momentum transfers of $Q^{2} = 4.5 \pm 0.5$ (GeV/c)$^{2}$
  reaching neutron recoil (missing) momenta up $p_{\mathrm{r}}\sim$ 1.01 GeV/c. The data have been obtained at fixed neutron recoil angles
$\theta_{nq} = 35^\circ$ and $45^\circ$  with respect to the 3-momentum
transfer $\vec q$. At these kinematic settings final state interactions (FSI),
meson exchange currents (MEC) and isobar configurations (IC) are expected to 
be suppressed and the plane wave impulse approximation (PWIA) provides the
dominant cross section contribution. The new data are compared to recent
theoretical calculations where a significant disagreement at very high
missing momenta has been observed.
